---
title: "lab 11"
author: "Matt Crump"
date: "12/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)
```


An X and Y variable contain the above numbers.

1. 
A. Compute Pearson’s r and report the associated p-value using the cor.test() function. (2 points)

```{r}
cor.test(X,Y)
```


B. Use a permutation test to create a null-distribution, and report the p-value for getting the observed correlation or larger using your simulated null-distribution. (2 points)

```{r}

# generate null-distribution of r values
sim_rs <- replicate(10000,cor(sample(X),sample(Y)))
#hist(sim_rs)

length(sim_rs[sim_rs >= cor(X,Y)])/10000

```


2. Using the variables X and Y above, and assuming that the values could be re-ordered in any way, report the following:

A. the smallest possible sum of cross-products (1 point)

```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)

sum(X*Y)

sort(X)
sort(Y, decreasing = TRUE)

sum(sort(X)*sort(Y, decreasing = TRUE))

```


B. the largest possible sum of cross-products (1 point)

```{r}
sum(sort(X)*sort(Y))
```



