---
title: "Lab 11"
author: "Matt Crump"
date: "12/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```


```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)
```

1. An X and Y variable contain the above numbers.

   A. Compute Pearson's $r$ and report the associated p-value using the `cor.test()` function. (2 points)
   
```{r}
(my_cor <- cor.test(X,Y))
```
   
The correlation was $r$ = `r my_cor$estimate`, $p$ = `r my_cor$p.value`.

The correlation was $r$ = `r round(my_cor$estimate,digits=2)`, $p$ = `r round(my_cor$p.value,digits=2)`.

We found a positive correlation, `r papaja::apa_print(my_cor)$full_result`.

   B. Use a permutation test to create a null-distribution, and report the p-value for getting the observed correlation or larger using your simulated null-distribution. (2 points)
   
```{r}
sim_rs <- replicate(1000,cor(sample(X),sample(Y)))
hist(sim_rs)

length(sim_rs[sim_rs >= my_cor$estimate]) / 1000

```
   

2. Using the variables X and Y above, and assuming that the values could be re-ordered in any way, report the following:

   A. the smallest possible sum of products (1 point)

```{r}
sum(sort(X)*sort(Y, decreasing =TRUE))
```

   B. the largest possible sum of products (1 point)

```{r}
sum(sort(X)*sort(Y))
```
