---
title: "testlab8"
author: "Matt Crump"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.

```{r}

# write what the function does

# compute mean and sd from scores
some_numbers <- c(1,2,3,4,5)
mean(some_numbers)
sd(some_numbers)

(some_numbers-mean(some_numbers))/sd(some_numbers)

# compute zscores from known mu and sd
some_numbers <- c(1,2,3,4,5)
mu <- 3
sigma <- 1
(some_numbers-mu)/sigma


# put it into a function

raw_to_zscores <- function(raw_scores,mu,sigma){
  z_scores <- (raw_scores-mu)/sigma
  return(z_scores)
}

raw_to_zscores(raw_scores = c(1,2,3,4,5),
               mu = 3,
               sigma = 1)

raw_to_zscores(raw_scores = c(1,2,3,4,5),
               mu = 5.25,
               sigma = 1)

```

2. Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).

- Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).

```{r}

z.test <- function(sample_mean, sample_size, mu, sigma){
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  p_value <- pnorm(sample_mean,smpl_dist_mean,smpl_dist_sd, lower.tail=FALSE)
  return(p_value)
}

z.test <- function(sample_mean,sample_size,mu,sigma){
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  p_value <- pnorm(sample_mean,smpl_dist_mean,smpl_dist_sd, lower.tail=FALSE)
  return(p_value)
}

z.test(sample_mean = 50,
       sample_size = 25,
       mu = 40,
       sigma = 7)

```


