---
title: "Lab 10"
author: "Matt Crump"
date: "3/17/2021"
bibliography: BCStats.bib
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. From Chapter 20, reproduce the bat and hat example (20.2) in R. Your code should represent the data in long-form, conduct the ANOVA, and report the ANOVA table. You will know if you did it correctly if you can reproduce the ANOVA table from the textbook. (3 points)

```{r}
# option 1
# write the whole thing by hand as a tribble

library(tibble)

bat_hat_data <- tribble(~Subject, ~Phonological_Similarity, ~Age, ~num_correct,
        "s1","b1","a1",15,
        "s2","b1","a1",23,
        "s3","b1","a1",12,
        "s4","b1","a1",16,
        "s5","b1","a1",14,
        "s1","b2","a1",13,
        "s2","b2","a1",19,
        "s3","b2","a1",10,
        "s4","b2","a1",16,
        "s5","b2","a1",12,
        "s6","b1","a2",39,
        "s7","b1","a2",31,
        "s8","b1","a2",40,
        "s9","b1","a2",32,
        "s10","b1","a2",38,
        "s6","b2","a2",29,
        "s7","b2","a2",15,
        "s8","b2","a2",30,
        "s9","b2","a2",26,
        "s10","b2","a2",30,
        )

## conduct ANOVA

aov_out <- aov( num_correct ~ Phonological_Similarity*Age + Error(Subject/Phonological_Similarity), data = bat_hat_data)
summary(aov_out)

## Option 2
# construct the data frame with functions

Subject <- c(rep(c("s1","s2","s3","s4","s5"),2),
             rep(c("s6","s7","s8","s9","s10"),2))
Phonological_Similarity <- rep(rep(c("b1","b2"), each=5),2)
Age <- rep(c("a1","a2"), each=10)
num_correct <- c(15,23,12,16,14,
                 13,19,10,16,12,
                 39,31,40,32,38,
                 29,15,30,26,30)

bat_hat_data <- tibble(Subject,
                       Phonological_Similarity,
                       Age,
                       num_correct)

# run ANOVA
aov_out <- aov( num_correct ~ Phonological_Similarity*Age + Error(Subject/Phonological_Similarity), data = bat_hat_data)
summary(aov_out)

```

2. From Chapter 21, reproduce the phonological similarity example (21.2.1) in R. Your code should represent the data in long-form, conduct the ANOVA, and report the ANOVA table. You will know if you did it correctly if you can reproduce the ANOVA table from the textbook. (3 points) Note, the F-value for the phonological similarity factor that you find with R may not be the same as the textbook. The textbook produces the quasi-F, and it is OK if you do not.

```{r}
# get the data into R in long format
subject <- rep(c("s1","s2","s3","s4"), each=10)
Typicality_B <- rep(rep(c("b1","b2"), each=5),4)
Faces_A <- rep(c("a1","a2","a3","a4","a5"),8)

#Faces_A <- rep(c("a1","a2","a3","a4","a5",
#                 "a6","a7","a8","a9","a10"),4)

centiseconds <- c(20,22,25,24,19,37,37,43,48,45,
                   9,8,21,21,21,34,35,35,37,39,
                   18,20,18,21,33,35,39,39,37,40,
                   5,14,16,22,23,38,49,51,50,52)

face_data <-  tibble(subject,
                     Typicality_B,
                     Faces_A,
                     centiseconds)

# run the anova
aov_out <- aov(centiseconds  ~ (subject + 
                                Faces_A%in%Typicality_B + 
                                Typicality_B + 
                                Typicality_B:subject),
               data = face_data)

summary(aov_out)
```

Bonus points:

3. Use R to produce the missing quasi_F value for problem 2. 

```{r}

```

