---
title: "Lab 1"
author: "Matt Crump"
date: "8/26/2020"
bibliography: BCStats.bib
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Written QALMRI

This is a QALMRI for @slameckaRetroactiveInhibitionConnected1960.

### Q

 - asdljfnadskjhf

### A

- asdljfnadskjhf
- asdljfnadskjhf

### L

- asdljfnadskjhf

### M

- asdljfnadskjhf

### R

- asdljfnadskjhf

### I

- asdljfnadskjhf

## Coding Problem

1. Create a dataframe that capable of representing the design, in as complete a way as you can, in the @slameckaRetroactiveInhibitionConnected1960 paper.


```{r}
library(tibble)

n <- 36
OL <- 3
IL <- 3

design <- matrix(4,ncol=3, nrow=3)
colnames(design) <- c("OL_2","OL_4","OL_8")
row.names(design) <- c("IL_0","IL_4","IL_8") 

36/9

# between-subjects version

subjects <- 1:36
OL <- rep(c(2,4,8),12)
IL <- rep(c(0,4,8), each=12)
recall <- sample(0:20,36, replace=TRUE)

long_design <- tibble(subjects,
                      OL,
                      IL,
                      recall)

library(dplyr)
long_design %>%
  group_by(OL,IL)%>%
  count()

# mixed design

mixed_design <- tribble(
  ~Subjects, ~OL, ~IL,
  #--|--|----
  1, 2, 0,
  1, 4, 4,
  1, 8, 8,
  2, 4, 0,
  2, 8, 4,
  2, 2, 8,
  3, 8, 0,
  3, 2, 4,
  3, 4, 8,
  4, 2, 4,
  4, 4, 0,
  4, 8, 8,
  5, 4, 4,
  5, 2, 8,
  5, 8, 0,
  6, 8, 4,
  6, 4, 8,
  6, 2, 0,
  7, 2, 8,
  7, 4, 0,
  7, 8, 4,
  8, 4, 8,
  8, 2, 4,
  8, 8, 0,
  9, 8, 8,
  9, 4, 4,
  9, 2, 0
)

mixed_design %>%
  group_by(OL,IL)%>%
  count()

full_mixed_design <- rbind(mixed_design,
                           mixed_design,
                           mixed_design,
                           mixed_design) %>%
  mutate(Subjects = rep(1:36, each=3),
         recall = sample(0:20,36*3, replace=TRUE))

full_mixed_design %>%
  group_by(OL,IL) %>%
  summarize(mean_recall = mean(recall), .groups="drop")

```



## References


