---
title: "Lab 6"
author: "Matt Crump"
date: "3/17/2021"
bibliography: BCStats.bib
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Section 12.3.3 from your textbook refers to: The problem with replications of a meaningless experiment: 'alpha and the captain's age'. The issue here is that if you run an ineffectual experiment enough times you can always find a significant result by chance. The textbook mentions that if you repeat an experiment 20 times, you are guaranteed to find a significant result with .64 probability, and the probability is .92 if you repeat the experiment 50 times.

a. Make use of the `rbinom()` function to show you can reproduce both probabilities. (1 point)

```{r}

A <- replicate(10000,sum(rbinom(20,1,.05)))
hist(A)

length(A[A > 0])/10000

B <- replicate(10000,sum(rbinom(50,1,.05)))
hist(B)

length(B[B > 0])/10000

```



b. If the ineffectual experiment was conducted 20 times, and there were four groups, and the experimenter would accept a significant result from any of the orthogonal linear contrasts, what would be the probability of finding a significant result here? (1 point)

```{r}

D <- replicate(10000,sum(rbinom(20,3,.05)))

length(D[D > 0])/10000

```

The next two questions draw a connection to a technique we have not yet discussed called p-curve analysis. P-curve analysis is sometimes used for purposes of meta-analyses to determine whether there is "good" evidence for an effect in the literature.

2. Consider that a researcher publishes a study showing a significant effect, p <. 05; but, in reality the researcher makes a type I error, and the manipulation did not cause any difference. If many other researchers replicated the study, what kind of p-values would they find? Use R to create a sampling distribution of p-values that would be expected in this situation. What shape does this distribution have? (2 points)

```{r}
library(tibble)

# my_pvalues <- c()
# 
# for(i in 1:10000){
# 
#   IV <- rep(1:2,each=20)
#   DV <- c(rnorm(20,0,1),rnorm(20,0,1))
#   
#   sim_data <- tibble(IV,DV)
#   
#   my_pvalues[i] <- t.test(DV~IV, var.equal=TRUE,  data = sim_data)$p.value
#   
# }
# 
# hist(my_pvalues)

my_pvalues <- replicate(10000,t.test(rnorm(20,0,1),rnorm(20,0,1), var.equal=TRUE)$p.value)

hist(my_pvalues)

```


3. Now assume that the published result reflects a true effect. Specifically, let's imagine the study had two groups (between-subjects), with 20 subjects in each group. Assume that scores for subjects are all sampled from a normal distribution, and that group A has larger mean than group B by .5 standard deviations (e.g., Cohen's d = .5). If many other researchers replicated the study, what kind of p-values would they find? Use R to create a sampling distribution of p-values that would be expected in this situation. What shape does this distribution have? (2 points) 

```{r}
my_pvalues <- replicate(10000,t.test(rnorm(20,0.5,1),rnorm(20,0,1), var.equal=TRUE)$p.value)

hist(my_pvalues)
```

Bonus Questions

4. Same as #3, except that we now assume the design has four groups (between-subjects). Assume that group A has a mean that is .5 standard deviations larger than groups B, C, and D. Use R to create a sampling distribution of p-values that would be expected for the linear contrast evaluating the research hypothesis that A > B = C = D. (1 point)


```{r}
my_pvalues <- c()

for(i in 1:1000){

  IV <- factor(rep(1:4,each=20))
  DV <- c(rnorm(20,0.5,1),rnorm(20,0,1),rnorm(20,0,1),rnorm(20,0,1))

  sim_data <- tibble(IV,DV)
  
  c1 <- c(3, -1,-1,-1)
  
  contrasts(sim_data$IV) <- c1
  
  aov.out <- aov(DV~IV, sim_data)
  
  save_results <- summary.aov(aov.out, split = list(IV=list("c1" =1)))

  my_pvalues[i] <- save_results[[1]]$`Pr(>F)`[2]

}

hist(my_pvalues)
```


5. Consider a one-factor between subjects ANOVA with four groups. Run two simulations of the null-hypothesis, one for the omnibus test, and one for the specific linear contrast mentioned above A > B = C = D. Is the probability of making a type I error (for rejecting the null with alpha < .05) the same for the omnibus test versus a specific contrast? (1 point)

```{r}

omnibus_pvalues <- c()
contrast_pvalues <- c()

for(i in 1:1000){

  IV <- factor(rep(1:4,each=20))
  DV <- c(rnorm(20,0,1),rnorm(20,0,1),rnorm(20,0,1),rnorm(20,0,1))

  sim_data <- tibble(IV,DV)
  
  c1 <- c(3, -1,-1,-1)
  
  contrasts(sim_data$IV) <- c1
  
  aov.out <- aov(DV~IV, sim_data)
  
  save_results <- summary.aov(aov.out, split = list(IV=list("c1" =1)))

  omnibus_pvalues[i] <- save_results[[1]]$`Pr(>F)`[1]
  contrast_pvalues[i] <- save_results[[1]]$`Pr(>F)`[2]

}

length(omnibus_pvalues[omnibus_pvalues < .05])/1000
length(contrast_pvalues[contrast_pvalues < .05])/1000


```
















